### 2010-03-25 docs/architecture/architecture.tex
reorganization
another reorg fix
add reference

@@

\section{Adding A Problem}

Different problems in MAESTRO are contained in individual
sub-directories under {\tt MAESTRO/}.  The minimum requirement to
define a new problem would be a {\tt GNUmakefile} which describes how
to build the application and an input file which lists the runtime
parameters.  The problem-specific executable is built in the problem
directory by typing {\tt make}.  Source files are found automatically
by searching the directories listed in the {\tt GNUmakefile}.

>>>>

\section{Running A Problem}

Different problems in MAESTRO are contained in individual
sub-directories under {\tt MAESTRO/}.  The {\tt GNUmakefile}
in each problem directory lists the components of {\tt MAESTRO}
that are used to build the executable.  Full details of the
{\tt GNUmakefile} can be found in \S~\ref{sec:adding_problems}.

Some of the test problems available are:
\begin{itemize}
\item {\tt flame}
\item {\tt planar\_heat}
\item {\tt spherical\_heat}
\item {\tt test2}
\item {\tt test\_convect}
\item {\tt test\_spherical}
\end{itemize}

\subsection{Unit Tests}

In addition to the problems descibed above which use the full
capabilities of MAESTRO, there are a number of unit tests that
exercise only specific components of the MAESTRO solvers.  The
tests have their own drivers (a custom {\tt varden.f90}) that
initialize only the data needed for the specific test and call
specific MAESTRO routines directly.

\begin{itemize}
\item {\tt test\_advect} \\[-3mm]

  This test initializes a Gaussian density field (no other scalar
  quantities are used) and a uniform velocity field in any one of the
  coordinate directions.  The Gaussian profile is advected through
  the period domain exactly once and the error in the density profile
  (L2 norm) is computed.  The driver for this problem does this 
  for every dimension twice (once with a positive velocity and once
  with a negative velocity).  After all coordinate directions are 
  tested, the norms are compared to ensure that the error does
  not show any directional bias.

\item {\tt test\_average} \\[-3mm]

  This test initializes a 1-d radial base state quantity with a
  Gaussian distribution, maps it into the 3-d domain (assuming a
  spherical geometry) using the routines provided by the {\tt
    fill\_3d\_module} module, and then calls {\tt average} to put it
  back onto a 1-d radial array.  This way we test the accuracy of our
  procedure to map between the 1-d radial and 3-d Cartesian states.
  The output from this test was described in detail in
  \cite{multilevel}.

\item {\tt test\_basestate}
\item {\tt test\_diffusion}
\end{itemize}

\section{Adding A New Problem}
\label{sec:adding_problems}

The minimum requirement to
define a new problem would be a {\tt GNUmakefile} which describes how
to build the application and an input file which lists the runtime
parameters.  The problem-specific executable is built in the problem
directory by typing {\tt make}.  Source files are found automatically
by searching the directories listed in the {\tt GNUmakefile}.

@@
